### 2021-11-13 NSF2021/Description/specificaim2.tex
fingers crossed

\begin{wrapfigure}[27]{l}{1.8in}
  \vspace{-4pt}
  \centering
  \input{figures/doublewell.tikz} 
  \caption{\label{fig:CA} (a) The double well potential $u_0 =
  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
  and inexact Newton's methods.}
\end{wrapfigure}
Having demonstrated that the inexact Newton method converges in one
dimension, it will be coupled with IE formulations to to
solve~\eqref{eq:SL} in two and three dimensions. We first partition
$\Omega$ into $\Omega_0 = \{\xx \in \Omega \:|\: u(\xx) < (u_0 +
u_1)/2\}$ and $\Omega_1 = \{\xx \in \Omega \:|\: u(\xx) > (u_0 +
u_1)/2\}$, and we let $\Lambda = \{\xx \in \Omega \:|\: u(\xx) = (u_0 +
u_1)/2 \}$ be their common boundary, and we let $G_0$ be the fundamental
solution of $(-\rho^2 \Delta - 2a)$ and $G_1$ be the fundamental
solution of $(-\rho^2 \Delta + 2)$. Then, the solution
of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$ where
$u^P$ is a volume potential and $u^H$ is a layer potential. The volume
potential is
\begin{align*}
  u^{P}(\xx) = \int_{\Omega_i} G_i(\xx,\yy) J[u^N](\yy)\, d\yy, 
    \quad i = 1,2,
\end{align*}
but it is discontinuous across $\Lambda$ and does not satisfy the
prescribed hydrophobic boundary conditions on the particles $\Gamma_i$.
Assuming the particles are entirely contained in the hydrophobic region,
the boundary conditions will be enforced with the layer potentials
\begin{align*}
  u^{H}(\xx) = \begin{cases}
    \displaystyle\int_{\Lambda} G_0(\xx,\yy) \eta_0(\yy) \, ds_\yy + 
    \displaystyle\int_{\Gamma} \pderiv{}{\nn_\yy} G_0(\xx,\yy)
      \sigma(\yy) \,ds_\yy, \quad & \xx \in \Omega_0, \\
    \displaystyle\int_{\Lambda} G_1(\xx,\yy) \eta_1(\yy) \, ds_\yy,
     & \xx \in \Omega_1.
  \end{cases}
\end{align*}
The density functions $\sigma$, $\eta_0$, and $\eta_1$ are determined so
that $u = u^P + u^H$ satisfies the hydrophobic boundary condition on
$\Gamma = \cup_i \Gamma_i$, and that it is continuous and differentiable
across $\Lambda$. This approach for using IEs to solve elliptic PDEs
with with piecewise constant coefficients has succesfully been used in
other application such as scattering~\cite{hyu-bar2014,
che-cho-cai2018}.

>>>>

%\begin{wrapfigure}[27]{l}{1.8in}
%  \vspace{-4pt}
%  \centering
%  \input{figures/doublewell.tikz} 
%  \caption{\label{fig:CA} (a) The double well potential $u_0 =
%  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
%  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
%  and inexact Newton's methods.}
%\end{wrapfigure}
Having demonstrated that the inexact Newton method converges in one
dimension, it will be coupled with IE formulations to to
solve~\eqref{eq:SL} in two and three dimensions. We first partition
$\Omega$ into $\Omega_0 = \{\xx \in \Omega \:|\: u(\xx) < (u_0 +
u_1)/2\}$ and $\Omega_1 = \{\xx \in \Omega \:|\: u(\xx) > (u_0 +
u_1)/2\}$, and we let $\Lambda = \{\xx \in \Omega \:|\: u(\xx) = (u_0 +
u_1)/2 \}$ be their common boundary, and we let $G_0$ be the fundamental
solution of $(-\rho^2 \Delta - 2a)$ and $G_1$ be the fundamental
solution of $(-\rho^2 \Delta + 2)$. Then, the solution
of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$ where
$u^P$ is a volume potential and $u^H$ is a layer potential. The volume
potential is
\begin{align*}
  u^{P}(\xx) = \int_{\Omega_i} G_i(\xx,\yy) J[u^N](\yy)\, d\yy, 
    \quad i = 1,2,
\end{align*}
but it is discontinuous across $\Lambda$ and does not satisfy the
prescribed hydrophobic boundary conditions on the particles $\Gamma_i$.
Assuming the particles are entirely contained in the hydrophobic region,
the boundary conditions will be enforced with the layer potentials
\begin{align*}
  u^{H}(\xx) = \begin{cases}
    \displaystyle\int_{\Lambda} G_0(\xx,\yy) \eta_0(\yy) \, ds_\yy + 
    \displaystyle\int_{\Gamma} \pderiv{}{\nn_\yy} G_0(\xx,\yy)
      \sigma(\yy) \,ds_\yy, \quad & \xx \in \Omega_0, \\
    \displaystyle\int_{\Lambda} G_1(\xx,\yy) \eta_1(\yy) \, ds_\yy,
     & \xx \in \Omega_1.
  \end{cases}
\end{align*}
The density functions $\sigma$, $\eta_0$, and $\eta_1$ are determined so
that $u = u^P + u^H$ satisfies the hydrophobic boundary condition on
$\Gamma = \cup_i \Gamma_i$, and that it is continuous and differentiable
across $\Lambda$. This approach for using IEs to solve elliptic PDEs
with with piecewise constant coefficients has succesfully been used in
other application such as scattering~\cite{hyu-bar2014,
che-cho-cai2018}.
